Modeling vertical-axis cross-flow turbine wakes

### 2015-03-19 paper.tex
Add questions to introduction
Add comments on model verification

@@

@@

@@

Predictions for both the power and drag coefficients are shown in Figure~\ref{fig:perf_comp}

\begin{figure}
\caption{Power (a) and drag (b) coefficient predictions from experiments and
each numerical model.}
\label{fig:perf_comp}
\end{figure}

>>>>

Questions addressed:

\begin{enumerate}

    \item Can 2-D RANS be used for array design?

    \item Can ALM--RANS be used for array design?

    \item Does 3-D RANS tell us more about what is happening, i.e, can it
    ``interpolate'' the experimental results?

\end{enumerate}

@@

The RANS models employ a sliding mesh, where the turbine zone rotates at a mean
tip speed ratio $\lambda=1.9$ with an unsteadiness as the blade passage
frequency specified to mimic the experimental data.

To capture the boundary layer,

@@

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in 
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen.

\begin{figure}[ht]
\caption{Spatial grid dependence for the SST (a) and Spalart--Allmaras (b) 
turbulence models for fixed timesteps.}
\label{fig:spatial-grid-dep}
\end{figure}

Timestep dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing timestep, leading to a
final timestep of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002 s$, which was the final timestep chosen to run the
simulations.

\begin{figure}[ht]
\caption{Spatial grid dependence for the SST (a) and Spalart--Allmaras (b) 
turbulence models for a grid with $N_x=70$.}
\label{fig:timestep-dep}
\end{figure}

@@

Predictions for both the power and drag coefficients are shown in Figure~\ref{fig:perf-comp}

\begin{figure}[ht]
\caption{Power (a) and drag (b) coefficient predictions from experiments and
each numerical model.}
\label{fig:perf-comp}
\end{figure}
